---
title: "EED-Stress results"
author: "Andrew Mertens"
date: "2024-03-24"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(knitr)
library(DT)

forest_plots <- readRDS(paste0(here::here(),"/figure-data/forest_plots.rds"))
heatmaps <- readRDS(paste0(here::here(),"/figure-data/heatmaps.rds"))
tables <- readRDS(paste0(here::here(),"/tables/results-table-objects.rds"))



d <- readRDS(file=paste0(here::here(),"/results/adjusted/adjusted_res.RDS"))

d14 <- d %>% filter(time=='14 months')
d28 <- d %>% filter(time=='28 months')

```

## Results interpretations

Nothing is significant after correcting for multiple comparisons, so weak to no association between EED and stress outcome

Looks like Alpha-1 antitrypsan has the strongest associations with stress - specifically cortisol and salivary amalyase, but in opposite directions. I think cortisol and amalyase should both increase with stress, so interesting and hard to interpret finding. Ask Audrie, but could be random chance.


## Figures

### Consort figure

(to add)

### Heatmaps - adjusted analyses

Primary figures
To do: scale point estimates, and add figure legends

### Figure 1 -Heatmap of adjusted association's direction and significance for year 1 measurements

Cells are colored by the direction and P-value significance for each EED exposure and stress outcome combination. Printed in each cell is the  point estimate from adjusted regression models. Each row is a specific stress outcome and each column is an EED exposure.

```{r, echo=FALSE}

heatmaps$p_heatmap14

```

### Figure 2 -Heatmap of adjusted association's direction and significance for year 2 measurements

Cells are colored by the direction and P-value significance for each EED exposure and stress outcome combination. Printed in each cell is the  point estimate from adjusted regression models. Each row is a specific stress outcome and each column is an EED exposure.


```{r, echo=FALSE}

heatmaps$p_heatmap28

```


### Heatmaps - unadjusted analyses

-supplimentary figures

```{r, echo=FALSE}

heatmaps$p_heatmap14_unadj
heatmaps$p_heatmap28_unadj

```



### Forest plots

(adjusted results only)
To do: format labels
```{r, echo=FALSE}

forest_plots$p_14mo
forest_plots$p_28mo
```

### Spline plots

Supplementary plots: to add for key significant relationships


## Tables

-Note I'm splitting the tables by domain of stress outcome (consistent with prior stress papers from this study)

### EED biomarker adjusted associations with year-1 oxidative stress measures

Biomarkers measured at child age 14 months

```{r, echo=FALSE}

#DT::datatable(d14, options = list(autoWidth = TRUE))

knitr::kable(tables$tab_ox_stress)

```

### EED biomarker adjusted associations with year-2 sympathetic adrenomedullary axis measures

```{r, echo=FALSE}

knitr::kable(tables$tab_spa)

```

### EED biomarker adjusted associations with year-2 hypothalamic-pituitary-adrenal axis measures


```{r, echo=FALSE}

knitr::kable(tables$tab_hpa)

```